**Density Dependence**

### 2023-03-10 Rmd/report whb.Rmd
\@\@ addresed

&nbsp;

@@

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

@@

[@@ The fixed maturity ogive for blue whiting is derived from ...]

@@

The distribution of mass-at-age is shown in the figure below (left) and the relationship between mass-at-age and total biomass is shown to the right.

[@@ Consistent negative slopes on the biomass-mass-at-age plots can be observed for ages 4 and beyond. The patterns for the younger ages are less clear. It should be remembered that the younger ages do not appear strongly in the catches.]

@@

[@@Negative slopes on the biomass-maturity-at-age plots can be observed for ages 2 and 3, which are the most relevant ages for maturity as all fish of age 4 and above are mature.]

@@

[@@This value was calculated based on estimates of total mortality derived from tagging data combined with catch data.]

@@

This work was funded under a consultancy agreement between the University of Copenhagen and `r ifelse(mystk=="mac", "Martin Pastoors F&F", "Sea++")` as part of the project “117957 Fmsy-project for six high profile fish stocks”. The current work focused on `r mystkname` and was carried out in the months of January-March 2023. A similar project was carried out for `r ifelse(mystk=="mac", "Blue whiting", mystkname)` by `r ifelse(mystk=="mac", "Sea++", "Martin Pastoors F&F")`. Both projects were carried in close coordination between Sea++ and Martin Pastoors F&F.

>>>>

@@

@@

The fixed maturity ogive for blue whiting was taken from the ICES assessment, this did not vary by year.

@@

The variation in mass-at-age is shown in the figure below (left) and the relationship between mass-at-age and total biomass  to the right. Consistent negative slopes on the biomass-mass-at-age plots are seen for ages 4 and beyond. The patterns for the younger ages, however, are less clear. The younger ages do not appear strongly in the catches, and so the catches may not be representative of the population.

@@

[\@ @Negative slopes on the biomass-maturity-at-age plots can be observed for ages 2 and 3, which are the most relevant ages for maturity as all fish of age 4 and above are mature.]

@@

[\@ @This value was calculated based on estimates of total mortality derived from tagging data combined with catch data.]

@@

This work was funded under a consultancy agreement between the University of Copenhagen and `r ifelse(mystk=="mac", "Martin Pastoors F&F", "Sea++")` as part of the project "117957 Fmsy-project for six high profile fish stocks". The current work focused on `r mystkname` and was carried out in the months of January-March 2023. A similar project was carried out for `r ifelse(mystk=="mac", "Blue whiting", mystkname)` by `r ifelse(mystk=="mac", "Sea++", "Martin Pastoors F&F")`. Both projects were carried in close coordination between Sea++ and Martin Pastoors F&F.
